Considering scale in multilayer animal social networks

### 2020-06-22 paper/manuscript.Rmd
tidy

# Discussion
<!-- 1)
First, to what degree does the social scale of relationships, spatial
scale of landscapes, and temporal scale of analysis influence our ability to
interpret complex social systems? 
-->

<!-- 2)
Second, can variation in the social, spatial,
and temporal scale improve predictions associated with biological differences in
seasonal resource availability and social association?

+
We conclude with
perspectives for further development and application of scale in multilayer
networks with respect to phenotypes and individual fitness,
movement ecology and collective movement, and habitat selection
and space use.
-->

<!-- TODO: somewhere ref:ml -->

<!-- 
outline

@@

@@

box1: fitness
box2: extending qs

@@

# Box 2 
Silk et al. (2018) summarized some key multilayer questions in animal behaviour
research. While these questions are important for linking animal behaviour and
multilayer networks, we summarize our perspectives on the future of multilayer
networks with an additional set of questions posed through the lens of spatial
ecology that are relevant to the promise and problem of scale in multilayer
networks:

>>>>

# Discussion
<!-- 
outline

@@

TODO: somewhere ref:ml

@@

box1: fitness
box2: extending qs
-->

@@

# Box 2 
Silk et al. (2018) summarized some key multilayer questions in animal behaviour
research. While these questions are important for linking animal behaviour and
multilayer networks, we summarize our perspectives on the future of multilayer
networks with an additional set of questions posed through the lens of spatial
ecology that are relevant to scale in multilayer networks:
